Field training 02 - Leaf traits measurements

### 2023-06-13 submission_2/submission_2.qmd
changed data table

| Species | SPAD mean | SPAD stdv | chl Eq. 1 | chl Eq. 2 | chl Eq. 3 | chl Eq. 4 | chl Eq. 5 |
|---|---|---|---|---|---|---|---|
| Philadelphus Coronarius | 47.65 | 1.681434573 | 265.467675 | 621.573065 | 608.2915624 | 61.56568402 | 62.75488428 |
| Spirae Chamaedryfolia | 45.6 | 3.215932559 | 243.8084 | 584.63104 | 564.7495158 | 56.03685716 | 56.72252579 |
| Geranium molle | 36.1 | 3.919183588 | 155.5059 | 425.94494 | 386.0649413 | 36.23261347 | 35.51025089 |
| Alliaria petiolata | 27.64 | 1.416725489 | 93.583776 | 301.9521344 | 257.008503 | 24.57293509 | 23.40017292 |
| Geum urbanum | 28.03 | 2.746330886 | 96.092139 | 307.3093226 | 262.3688604 | 25.01677595 | 23.85444116 |
| Ballota nigra | 38.44 | 4.576558629 | 175.413216 | 463.1218304 | 426.6499938 | 40.34089174 | 39.8524312 |
| Geranium sanguineum | 48.9 | 6.534332407 | 279.1283 | 644.56894 | 635.7441646 | 65.20131502 | 66.7438002 |
| Acer platanoides | 31.59 | 5.872998477 | 120.535811 | 357.8139034 | 313.8933755 | 29.4575616 | 28.43095204 |

>>>>

| Species | SPAD mean | SPAD stdv | chl Eq. 1 | chl Eq. 2 | chl Eq. 3 | chl Eq. 4 | chl Eq. 5 |
|---|---|---|---|---|---|---|---|
| Philadelphus Coronarius | 47.65 | 1.681434573 | 26.5467675 | 55.53686838 | 54.35018076 | 61.56568402 | 62.75488428 |
| Spirae Chamaedryfolia | 45.6 | 3.215932559 | 24.38084 | 52.23613916 | 50.45974688 | 56.03685716 | 56.72252579 |
| Geranium molle | 36.1 | 3.919183588 | 15.55059 | 38.057711 | 34.49447706 | 36.23261347 | 35.51025089 |
| Alliaria petiolata | 27.64 | 1.416725489 | 9.3583776 | 26.97909046 | 22.96342652 | 24.57293509 | 23.40017292 |
| Geum urbanum | 28.03 | 2.746330886 | 9.6092139 | 27.45774932 | 23.44236855 | 25.01677595 | 23.85444116 |
| Ballota nigra | 38.44 | 4.576558629 | 17.5413216 | 41.37942519 | 38.12070678 | 40.34089174 | 39.8524312 |
| Geranium sanguineum | 48.9 | 6.534332407 | 27.91283 | 57.59152447 | 56.80304051 | 65.20131502 | 66.7438002 |
| Acer platanoides | 31.59 | 5.872998477 | 12.0535811 | 31.97027796 | 28.04602719 | 29.4575616 | 28.43095204 |
